Tensor denoising and completion based on ordinal observations

### 2020-01-28 ICML/miaoyan/ordinalT.tex
udate

\begin{algorithm}[tb]
        \caption{Ordinal tensor decomposition ({\color{red} allowing missing data})}\label{alg}
        \begin{algorithmic}[]
            \STATE{\bfseries Input:}  \text{ Ordinal tensor }
            $\mathcal{Y}\in [L]^{d_1\times\cdots\times d_K}
            $,\\ \hspace{.43in} Rank $\mr\in \mathbb{N_+}^{K}$,\\
            \hspace{.43in} Entry-wise bound $\alpha\in \mathbb{R_+}$.
            \STATE{\bfseries Output:} $(\hat\Theta,\hat{\mb}) =  \argmax_{(\Theta,\mb)\in \mathcal{D}\times\mathcal{B}}  \mathcal{L}_{\mathcal{Y},\Omega}(\Theta,\mb).$
            \STATE Initialize  Core tensor $\mathcal{C}^{(0)}$,\\
            \hspace{.5in} Factor matrices $ \{\mM_1^{(0)},\cdots,\mM_K^{(0)}\}$,\\
            \hspace{.5in} Cut-off points $\mb^{(0)}$.
            \FOR{$t = 1,2,\cdots,$}
            \FOR{$k = 1,2,\cdots,K$}
            \STATE{Update $\mM_k$ while fixing other blocks:}
            \STATE $\mM_k^{(t+1)}\gets\argmax_{\mM_k\in\mathbb{R}^{d_k\times r_K}}\mathcal{L}_{\mathcal{Y},\Omega}(\mM_k)$,
            \newline
             s.t. $\mnormSize{}{\Theta^{(t+1)}}\leq \alpha$, where $\Theta^{(t+1)}$ is the parameter tensor based on the current block estimates. 
            \ENDFOR
            \STATE {Update $\mathcal{C}$ while fixing other blocks:}
            \STATE{$\mathcal{C}^{(t+1)} \gets \argmax_{\mathcal{C}\in \mathbb{R}^{r_1\times\cdots\times r_K}}\mathcal{L}_{\mathcal{Y},\Omega}(\mathcal{C})$, s.t. $\mnormSize{}{\Theta^{(t+1)}}\leq \alpha$}
               \STATE {Update $\Theta$ based on the current block estimates: 
               \STATE{$\Theta^{(t+1)} \gets \mathcal{C}^{(t+1)}\times_1\mM_1^{(t+1)}\cdots\times_K\mM_K^{(t+1)}$}
            \STATE {Update $\mb$ while fixing $\Theta^{(t+1)}$: \\
          \STATE{$\mb^{(t+1)} \gets \argmax_{\mb\in \mathbb{R}^{L-1}}\mathcal{L}_{\mathcal{Y},\Omega}\big(\Theta^{(t+1)},\mb\big)$}
            \ENDFOR
            \STATE \textbf{return}
            $\Theta,\mb$
        \end{algorithmic}
    \end{algorithm}

@@

\begin{table}[H]
\resizebox{\linewidth}{!}{%
\begin{tabular}{c|ccc|c}
\hline
\multirow{2}{*}{Critera}&\multicolumn{3}{c|}{Our method}&Continuous method\\
& $\hat y^{(\text{Mean})}_\omega$ & $\hat y^{(\text{Median})}_\omega$ & $\hat y^{(\text{Mode})}_\omega$ &~\cite{filipovic2015tucker}\\
\hline
MSE& 0.1504&  0.1504 & 0.1504&0.1604\\
MAD& 0.1503&0.1503 &0.1503&0.1600\\
MCR& 0.1503& 0.1502&0.1502& 0.1598\\
\hline
\end{tabular}
}
\caption{Comparison of tensor decomposition on HCP dataset.}
\end{table}

>>>>

\begin{algorithm}[tb]
        \caption{Ordinal tensor decomposition ({\color{red} allowing missing data})}\label{alg}
        \begin{algorithmic}[]
            \STATE{\bfseries Input:}  \text{ Ordinal tensor }
            $\mathcal{Y}\in [L]^{d_1\times\cdots\times d_K}
            $,\\ \hspace{.43in} Rank $\mr\in \mathbb{N_+}^{K}$,\\
            \hspace{.43in} Entry-wise bound $\alpha\in \mathbb{R_+}$.
            \STATE{\bfseries Output:} $(\hat\Theta,\hat{\mb}) =  \argmax_{(\Theta,\mb)\in \mathcal{D}\times\mathcal{B}}  \mathcal{L}_{\mathcal{Y},\Omega}(\Theta,\mb).$
            \STATE Initialize  Core tensor $\mathcal{C}^{(0)}$,\\
            \hspace{.5in} Factor matrices $ \{\mM_1^{(0)},\cdots,\mM_K^{(0)}\}$,\\
            \hspace{.5in} Cut-off points $\mb^{(0)}$.
            \FOR{$t = 1,2,\cdots,$}
            \FOR{$k = 1,2,\cdots,K$}
            \STATE{Update $\mM_k$ while fixing other blocks:}
            \STATE $\mM_k^{(t+1)}\gets\argmax_{\mM_k\in\mathbb{R}^{d_k\times r_K}}\mathcal{L}_{\mathcal{Y},\Omega}(\mM_k)$,
            \newline
             s.t. $\mnormSize{}{\Theta^{(t+1)}}\leq \alpha$, where $\Theta^{(t+1)}$ is the parameter tensor based on the current block estimates. 
            \ENDFOR
            \STATE {Update $\mathcal{C}$ while fixing other blocks:}
              \newline$\mathcal{C}^{(t+1)} \gets \argmax_{\mathcal{C}\in \mathbb{R}^{r_1\times\cdots\times r_K}}\mathcal{L}_{\mathcal{Y},\Omega}(\mathcal{C})$, s.t. $\mnormSize{}{\Theta^{(t+1)}}\leq \alpha$
               \STATE {Update $\Theta$ based on the current block estimates:} 
                   \newline
                   $\Theta^{(t+1)} \gets \mathcal{C}^{(t+1)}\times_1\mM_1^{(t+1)}\cdots\times_K\mM_K^{(t+1)}$
            \STATE {Update $\mb$ while fixing $\Theta^{(t+1)}$:}
              \newline
              $\mb^{(t+1)} \gets \argmax_{\mb\in \mathbb{R}^{L-1}}\mathcal{L}_{\mathcal{Y},\Omega}\big(\Theta^{(t+1)},\mb\big)$
            \ENDFOR
            \STATE \textbf{return}
            $\Theta,\mb$
        \end{algorithmic}
    \end{algorithm}

@@

\begin{table}[t]
\label{CV}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
 Method & RMSE & MAE & ERROR \\
\midrule
\begin{tabular}[c]{@{}c@{}}Oridnal tensor\\ Decomposition\end{tabular}  & 0.1504 & 0.1503& 0.1502 \\ \\
\begin{tabular}[c]{@{}c@{}}Conti tensor\\ Decomposition\end{tabular} & 0.1604& 0.1600& 0.1598\\ \\
\begin{tabular}[c]{@{}c@{}}1bit-completion\\ (probit)\end{tabular}  & 0.3658 & 0.3633 & 0.3620\\
\begin{tabular}[c]{@{}c@{}}1bit-completion\\ (logistic)\end{tabular}  &  0.4519& 0.4219 & 0.4068
\\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\caption{Results of comparisons among 4 methods on the HCP data predicting the test data. Four methods are the ordinal tensor decomposition algorithm, the continuous tensor decomposition algorithm and the 1 bit tensor completion method with probit link function and logistic link function. Each method is evaluated by RMSE, MAE, error(false prediction rate).}
\end{table}

%\begin{table}[H]
%\resizebox{\linewidth}{!}{%
%\begin{tabular}{c|ccc|c}
%\hline
%\multirow{2}{*}{Critera}&\multicolumn{3}{c|}{Our method}&Continuous method\\
%& $\hat y^{(\text{Mean})}_\omega$ & $\hat y^{(\text{Median})}_\omega$ & $\hat y^{(\text{Mode})}_\omega$ &~\cite{filipovic2015tucker}\\
%\hline
%MSE& 0.1504&  0.1504 & 0.1504&0.1604\\
%MAD& 0.1503&0.1503 &0.1503&0.1600\\
%MCR& 0.1503& 0.1502&0.1502& 0.1598\\
%\hline
%\end{tabular}
%}
%\caption{Comparison of tensor decomposition on HCP dataset.}
%\end{table}
